News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-23 rupnik2015.tex

\section{System Overview}

Event registry $\Rightarrow$ Monolingual events $\Rightarrow$ features (semantic + CCA) $\Rightarrow$ linked events (crosslingual)

@@

@@

The clustering of articles is done for each language separately -- English articles are, for example, clustered separately from Spanish articles. When events are identified, they will therefore be identified from clusters in each language separately. As a result, the same event will be represented in Event Registry with two or more event IDs, and each event will only contain coverage in a single language. To avoid this problem we want to exploit the available information about the similarity of the articles in a cluster with articles in other languages. Using this information we hope to be able to connect clusters in different languages and represent them using a single event ID.
\end{comment}

@@

>>>>

\section{Pipeline}

We base our techniques of cross-lingual event linking on an online system for detection of world events, called Event Registry\cite{}. Event Registry is a repository of events, where events are automatically identified by analyzing news articles.  Event Registry works by collecting and analyzing news articles that are published by news outlets in different languages all over the world. Collected articles are first semantically annotated by identifying in them mentions of relevant concepts -- either entities or important keywords. The disambiguated and entity linking of the concepts is done using Wikipedia as the main knowledge base. An online clustering algorithm is then applied on the articles in order to identify groups of articles that are discussing the same event. For each new article, the clustering algorithm determines if the article should be assigned to some existing cluster or into a new cluster. The underlying assumption is that articles that are describing the same event are similar enough and will therefore be put into the same cluster.

The processing is done independently for each language and the output is a clustering of articles in each language, with each cluster ideally representing an event, which are defined by topically, geographically and temporally. The goal of this paper is present approaches to  connecting the clusters/events across languages.

Our approach is based on first defining a similarity function between articles in different languages (Section~\ref{}) and then we present several efficient approaches to linking the clusters based on features (Section~\ref{}). First, however we describe the pre-processing on the input articles which we then take as input.

The system is designed to handle streams and so we describe how a document which enters the stream is processed.   A new document is first tokenized, stop words are removed and words are stemmed. 
 What remains is represented in a vector-space model and normalized using $TF-IDF$ (see Section~\ref{} for the definition). Since each article is tagged with its language, cosine similiarity  is used to find the modst similar existing cluster, by comparing it to the centroid vector of each cluster. A selected threshold is used to determine if the article is not similar to any existing clusters (0.4 was used in our experiments).  The article is then assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article.

The clusters, we consider must have a sufficient number of articles (which is a language dependent paramater). This is to ensure that we consider events. Once an event is identified(i.e. a cluster of sufficient size), a new unique ID is assigned to it and the main information about the event is then automatically extracted by analyzing the articles assigned to it. The extracted information includes properties such as the date of the event, the location, who is involved in it, what the event is about, etc.

 Further details about the system can be found in \cite{}, while our full pipeline is shown in Figure~\ref{}.

\begin{comment}
In short, the article clustering works as follows (details are available in \cite{}). First we create a new document by joining the title and the body of the article. We then tokenize the document, remove the stop words and stem the words. The remaining words are represented as a vector in the vector-space model. Each value in the vector is additionally normalized using TF-IDF. After normalization, we use the vector to find the most similar existing cluster. To be able to compare the vector with a cluster we first need a vector representation for each of the clusters. This is done by computing a centroid vector of the cluster by simply averaging the vectors of the articles in the cluster. By computing the cosine similarity of the article vector with each of the centroid vectors we then find the cluster with the highest similarity. If the highest similarity is above the selected threshold (we used 0.4 in our experiments),

In order to treat the cluster as describing an event in Event Registry,

The clustering of articles is done for each language separately -- English articles are, for example, clustered separately from Spanish articles. When events are identified, they will therefore be identified from clusters in each language separately. As a result, the same event will be represented in Event Registry with two or more event IDs, and each event will only contain coverage in a single language. To avoid this problem we want to exploit the available information about the similarity of the articles in a cluster with articles in other languages. Using this information we hope to be able to connect clusters in different languages and represent them using a single event ID.
\end{comment}
%Event registry $\Rightarrow$ Monolingual events $\Rightarrow$ features (semantic + CCA) $\Rightarrow$ linked events (crosslingual)

@@

The problem in the second phase of the pipeline is to identify the clusters describing the same events. Each article $a_i$ is written in a language $l$, where $\ell \in L = \{\ell_1,\ell_2,...,\ell_k\}$. For each language $\ell$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{\ell_a}$, we would like to identify clusters $c_j \in C_{\ell_b}$ (where $\ell_a \neq \ell_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{\ell_a}$ and $C_{\ell_b}$ respectively. Furthermore, we iterate over all the languages we consider. That is, given a cluster in language $\ell_i$, we look for matching clusters in language $\ell_j$ for $i\neq j$  in a pairwise fashion.

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage - that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem.

@@

The clustering of articles is done for each language separately -- English articles are, for example, clustered separately from Spanish articles. When events are identified, they will therefore be identified from clusters in each language separately. As a result, the same event will be represented in Event Registry with two or more event IDs, and each event will only contain coverage in a single language. To avoid this problem we want to exploit the available information about the similarity of the articles in a cluster with articles in other languages. Using this information we hope to be able to connect clusters in different languages and represent them using a single event ID.

@@

\end{comment}
